### 2021-07-20 chapters/10_related_work.tex
writing style issue

\chapter{Related work}
\label{ch:related_work}
Clustering mutants has been done before.
The research that exists tries to cluster mutants by defining the centroid of a cluster and cluster the mutants on that definition.
In our research extends mutation clustering by defining a centroid that is dynamic.
In other words the centroids of our clusters are defined by the mutants itself.

@@

\section{Clustering similarity}
Hussain et al., used the k-means and agglomerative clustering algorithm to cluster the mutants according to a similarity measure. 
They used the Hamming distance as similarity measure.
They calculated the distance and used this as data to feed into the clustering algorithms.
The number of clusters and the initial position of the cluster center in the k-means algorithm are difficult to determine, and the process of the agglomerative clustering algorithm makes it difficult to correct the existing cluster formation\cite{Hussain2008}.
They did take into account efficiency.
Hussain et al, had the same goals as our research. 
The difference is that our research used different and more elaborated methods to cluster the mutants.
Hussain et al., calculated the mutation score by counting one cluster as one mutant.
Our research calculated a weighted mutation score to reflect the clusters more accurately.

>>>>

\chapter{Related work}
\label{ch:related_work}
Clustering mutants has been done before.
The research that exists tries to cluster mutants by defining the centroid of a cluster and cluster mutants on that definition.
In our research extends mutation clustering by defining a centroid that is dynamic.
In other words the centroids of our clusters are defined by the mutants itself.

@@

\section{Clustering similarity}
Hussain et al., used the k-means and agglomerative clustering algorithm to cluster mutants according to a similarity measure. 
They used the Hamming distance as similarity measure.
They calculated the distance and used this as data to feed into the clustering algorithms.
The number of clusters and the initial position of the cluster center in the k-means algorithm are difficult to determine, and the process of the agglomerative clustering algorithm makes it difficult to correct the existing cluster formation\cite{Hussain2008}.
They did take into account efficiency.
Hussain et al, had the same goals as our research. 
The difference is that our research used different and more elaborated methods to cluster mutants.
Hussain et al., calculated the mutation score by counting one cluster as one mutant.
Our research calculated a weighted mutation score to reflect the clusters more accurately.

### 2021-07-20 chapters/2_introduction.tex
writing style issue

\section{Problem statement}
Mutation testing requires a significant amount of computational resources\cite{Kintis2016EffectiveMutation}. 
The high cost requirement is often a barrier for adopting mutation testing \cite{Pizzoleto2019}.
A lot of techniques and methods have been developed to improve the performance, however, most of these approaches are not as effective as mutation testing a full set of mutants\cite{Pizzoleto2019,Yao2014}. 
\newline
A technique to reduce the number of mutants or the number of test case executions is mutation clustering.
Mutation clustering aims to reduce the amount of mutants to be executed by clustering the mutants\cite{Ma2016,Yu2019PossibilityScope}.
Clustering is a technique used for the grouping of data, for pattern recognition and classification, based on some similar characteristics\cite{Alsabti1997}.
The clustering of mutants has been researched with promising results\cite{Ji2009,Wilinski2015,Ma2016}. For example Ma et al., \cite{Ma2016} clustered the mutants for expressions. 
However in their paper they indicate that the choosing expressions as the domain of their cluster is a limitation.
A recurring problem in the research of mutation clustering is to determine the means of domains as the centre of a cluster\cite{Ji2009,Wilinski2015,Ma2016,Wei2021SpectralTesting}.
\newline
To reduce the cost of mutation testing, we try to find a solution that can cluster mutants while maintaining the accuracy of the same complete set of mutants. 
Our goal is to cluster any mutant that is generated within the Java programming language.
This research aims to remove the scoping limitations present in existing research.
There should be no requirements for which mutants can be clustered.
We will do this with two different approaches: qualitative and quantitative. 
We structure our research on the following research questions:
\newline
\textbf{Research Question 1}: What set of characteristics can we identify for clustering generated mutants to reduce the amount executed, while maintaining effectiveness?
\newline
\textbf{Research Question 1.1}: How do the existing mutation testing tools for Java compare to each other?
\newline
\textbf{Research Question 2}: How can we train a machine learning model to recognize and cluster generated mutants to reduce the amount executed, while maintaining effectiveness?
\newline
We start with comparing existing mutation testing tools. 
We will use the existing literature as a starting point and research what would be the best tool to use for this thesis.
\newline
After we have selected a tool we will research existing clustering techniques.
Based on the results of this research we select and implement a clustering algorithm that will cluster one ore more characteristics of the mutants. 
We will randomly select on mutant per of each cluster to be executed by the mutation tooling.
We will then compare the mutation score of the clustered mutants with the mutation score of a full set of mutants.
\newline
To answer our second research question we will train a machine learning model to cluster mutants.
We can then repeat the comparison we did for research question one. 
\newline
We want to see how the algorithm/model performs on big and small projects.
These project must also require a test suite.
\newline
We chose to focus on projects that use Java as main programming language because it is one of the most popular languages\cite{Tiobe}.

@@

\section{Outline}
In Chapter~\ref{ch:background} we describe the background information of this thesis. 
Chapter \ref{ch:mutation-tool} compares the different mutation testing tools to decide on a tool to use for this research.
In chapter \ref{ch:reserach_question1} we identify characteristics to represent mutants and design an experiment to cluster them.
In chapter \ref{ch:reserach_question2} we select a machine learning model and design an experiment to cluster the mutants with this model.
Results are shown in Chapters \ref{ch:results_rq1} and \ref{ch:results_rq2} for the experiments described in Chapters \ref{ch:reserach_question1} and \ref{ch:reserach_question2} respectively. 
The results are then discussed in Chapter~\ref{ch:discussion}.
\newline
Chapter~\ref{ch:related_work}, contains the work related to this thesis.
Finally, we present our concluding remarks in Chapter~\ref{ch:conclusion} together with future work.

>>>>

\section{Problem statement}
Mutation testing requires a significant amount of computational resources\cite{Kintis2016EffectiveMutation}. 
The high cost requirement is often a barrier for adopting mutation testing \cite{Pizzoleto2019}.
A lot of techniques and methods have been developed to improve the performance, however, most of these approaches are not as effective as mutation testing a full set of mutants\cite{Pizzoleto2019,Yao2014}. 
\newline
A technique to reduce the number of mutants or the number of test case executions is mutation clustering.
Mutation clustering aims to reduce the amount of mutants to be executed by clustering mutants\cite{Ma2016,Yu2019PossibilityScope}.
Clustering is a technique used for the grouping of data, for pattern recognition and classification, based on some similar characteristics\cite{Alsabti1997}.
The clustering of mutants has been researched with promising results\cite{Ji2009,Wilinski2015,Ma2016}. For example Ma et al., \cite{Ma2016} clustered the mutants for expressions. 
However in their paper they indicate that the choosing expressions as the domain of their cluster is a limitation.
A recurring problem in the research of mutation clustering is to determine the means of domains as the centre of a cluster\cite{Ji2009,Wilinski2015,Ma2016,Wei2021SpectralTesting}.
\newline
To reduce the cost of mutation testing, we try to find a solution that can cluster mutants while maintaining the accuracy of the same complete set of mutants. 
Our goal is to cluster any mutant that is generated within the Java programming language.
This research aims to remove the scoping limitations present in existing research.
There should be no requirements for which mutants can be clustered.
We will do this with two different approaches: qualitative and quantitative. 
We structure our research on the following research questions:
\newline
\textbf{Research Question 1}: What set of characteristics can we identify for clustering generated mutants to reduce the amount executed, while maintaining effectiveness?
\newline
\textbf{Research Question 1.1}: How do the existing mutation testing tools for Java compare to each other?
\newline
\textbf{Research Question 2}: How can we train a machine learning model to recognize and cluster generated mutants to reduce the amount executed, while maintaining effectiveness?
\newline
We start with comparing existing mutation testing tools. 
We will use the existing literature as a starting point and research what would be the best tool to use for this thesis.
\newline
After we have selected a tool we will research existing clustering techniques.
Based on the results of this research we select and implement a clustering algorithm that will cluster one ore more characteristics of the mutants. 
We will randomly select on mutant per of each cluster to be executed by the mutation tooling.
We will then compare the mutation score of the clustered mutants with the mutation score of a full set of mutants.
\newline
To answer our second research question we will train a machine learning model to cluster mutants.
We can then repeat the comparison we did for research question one. 
\newline
We want to see how the algorithm/model performs on big and small projects.
These project must also require a test suite.
\newline
We chose to focus on projects that use Java as main programming language because it is one of the most popular languages\cite{Tiobe}.

@@

\section{Outline}
In Chapter~\ref{ch:background} we describe the background information of this thesis. 
Chapter \ref{ch:mutation-tool} compares the different mutation testing tools to decide on a tool to use for this research.
In chapter \ref{ch:reserach_question1} we identify characteristics to represent mutants and design an experiment to cluster them.
In chapter \ref{ch:reserach_question2} we select a machine learning model and design an experiment to cluster mutants with this model.
Results are shown in Chapters \ref{ch:results_rq1} and \ref{ch:results_rq2} for the experiments described in Chapters \ref{ch:reserach_question1} and \ref{ch:reserach_question2} respectively. 
The results are then discussed in Chapter~\ref{ch:discussion}.
\newline
Chapter~\ref{ch:related_work}, contains the work related to this thesis.
Finally, we present our concluding remarks in Chapter~\ref{ch:conclusion} together with future work.
